FMA: A Dataset For Music Analysis

### 2017-04-17 fma.tex
more figures

@@

@@

@@

% Collection
As of April 1st 2017, the date of collection, the online archive largest track id was 155,320, of which 109,727 were valid (the missing 45,594 ids probably correspond to deleted tracks). In addition to per-track metadata, the used hierarchy of 161 genres and extended album (480 not found) and artist (250 not found) information were collected via the available \href{https://freemusicarchive.org/api}{API}.\footnote{See \texttt{webapi.ipynb} to query the API with our helpers.}. Finally, mp3 audio was downloaded over HTTPS.
% Cleaning
Out of all collected track ids, 180 mp3s could not be downloaded, 286 could not be trimmed by ffmpeg, and features could not be extracted from 71. Finally, the license of 2,616 songs prohibited their redistribution, leaving us with \ntracks tracks.

@@

The collected track, album and artist meta-informations\footnote{Raw data is available in \texttt{raw\_tracks.csv}, \texttt{raw\_albums.csv}, and \texttt{raw\_artists.csv}.} were cleaned, uniformly formatted, merged and stored in \texttt{tracks.csv}\footnote{See \texttt{creation.ipynb} for the code which created the dataset.} which \tabref{tab:tracks} shows an excerpt. That file is a relational table where each rows represent a track. \tabref{tab:metadata} lists the collected song metadata and user data, although some values may be missing for some tracks. The audio for each track is stored in a file wich name is the track id. All songs are mp3-encoded, most of them with sampling rate of 44,100 Hz, bit rate 320 kb/s, and in stereo.
See the \texttt{analysis.ipynb} notebook for a much more detailed analysis of the content.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{genre_distribution.pdf}
	\caption{Power law distribution of the genres.}
	\label{fig:genre_distribution}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{genre_hierarchy.pdf}
	\caption{Example of genre hierarchy for the top-level Soul-RnB genre. Left number is the \texttt{genre\_id}, right number is the number of tracks.}
	\label{fig:genre_hierarchy}
\end{figure}

>>>>

\usepackage{caption}
%\captionsetup[figure]{skip=0pt}

@@

\begin{figure*}
	\begin{minipage}{0.74\linewidth}
		\centering
		\includegraphics[width=\linewidth]{growth.pdf}
	\end{minipage} \hfill
	\begin{minipage}{0.24\linewidth}
		\centering
		\includegraphics[width=\linewidth]{album_release_year.pdf}
	\end{minipage}
	\vspace{-1em}
	\caption{(Left) Growth of the archive, created in 2008. (Right) Number of albums released per year (1902-2017).}
	\label{fig:growth}
	\label{fig:album_release_year}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{duration_distribution.pdf}
	\caption{Gaussian distribution of track durations.}
	\label{fig:duration_distribution}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{listens_distribution.pdf}
	\caption{Power-law distribution of album play counts.}
	\label{fig:listens_distribution}
\end{figure}

@@

% Collection
As of April 1st 2017, the date of collection, the online archive largest track id was 155,320, of which 109,727 were valid (the missing 45,594 ids probably correspond to deleted tracks). See \figref{fig:growth} to visualize the growth of the dataset. In addition to per-track metadata, the used hierarchy of 161 genres and extended album (480 not found) and artist (250 not found) information were collected via the available \href{https://freemusicarchive.org/api}{API}.\footnote{See \texttt{webapi.ipynb} to query the API with our helpers.}. Finally, mp3 audio was downloaded over HTTPS.
% Cleaning
Out of all collected track ids, 180 mp3s could not be downloaded, 286 could not be trimmed by ffmpeg, and features could not be extracted from 71. Finally, the license of 2,616 songs prohibited their redistribution, leaving us with \ntracks tracks.

@@

The collected track, album and artist meta-informations\footnote{Raw data is available in \texttt{raw\_tracks.csv}, \texttt{raw\_albums.csv}, and \texttt{raw\_artists.csv}.} were cleaned, uniformly formatted, merged and stored in \texttt{tracks.csv}\footnote{See \texttt{creation.ipynb} for the code which created the dataset.} which \tabref{tab:tracks} shows an excerpt. That file is a relational table where each row represents a track and columns are listed in \tabref{tab:metadata}, although some values may be missing for some tracks. The audio for each track is stored in a file wich name is the track id. All songs are mp3-encoded, most of them with sampling rate of 44,100 Hz, bit rate 320 kb/s, and in stereo. Figures~\ref{fig:album_release_year},~\ref{fig:duration_distribution} and \ref{fig:listens_distribution} show the distribution of albums per year, track durations, and play counts per album.
See the \texttt{analysis.ipynb} notebook for a much more detailed analysis of the content.

@@

\begin{figure}
	\begin{minipage}[t]{0.44\linewidth}
		\centering
		\includegraphics[width=\linewidth]{genre_hierarchy.pdf}
	\end{minipage} \hfill
	\begin{minipage}[t]{0.55\linewidth}
		\centering
		\includegraphics[width=\linewidth]{genres_per_track.pdf}
	\end{minipage}
	\vspace{-1em}
	\caption{(Left) Example of genre hierarchy for the top-level Soul-RnB genre. Left number is the \texttt{genre\_id}, right number is the number of tracks per genre. (Right) Number of genres per track (\texttt{genres\_all}).}
	\label{fig:genre_hierarchy}
	\label{fig:genres_per_track}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{genre_distribution.pdf}
	\caption{Power law distribution of genres.}
	\label{fig:genre_distribution}
\end{figure}
